A large leading tail of atmospheric escape in the HAT-P-67 b system

### 2023-04-20 paper/paper1/ms.tex
Neat new figures on centroids

\subsection{Velocity substructure}
Figure \ref{fig:HeliumScanZoom} shows a zoom-in of the in-transit portion of the Helium excess absorption scan, overlaid with line center positions.  The scan appears to exhibit some velocity substructure.  At transit ingress, the absorption appears more centrally concentrated near the vertical 10833 \AA~ line.  The line depth gets slightly shallower with a slight redshift approaching transit mid-center. \authorcomment1{Add more text here and revise figure.}

\begin{figure}
    \includegraphics[width=\linewidth]{figures/phase_2D_diagram_zoom.png}
    \caption{A zoom-in of the in-transit and post-transit phase scan for the Helium 10830 triplet.  Some velocity substructure may be apparent.}
    \label{fig:HeliumScanZoom}
\end{figure}

>>>>

\subsection{Velocity substructure}
Figure \ref{fig:HeliumZoom} shows a zoom-in of the in-transit portion of the Helium excess absorption scan, overlaid with line center positions.  The scan appears to exhibit some velocity substructure.  At transit ingress, the absorption appears more centrally concentrated near the vertical 10833 \AA~ line.  The line depth gets slightly shallower with a slight redshift approaching transit mid-center. \authorcomment1{Add more text here and revise figure.}

%\begin{figure}
%    \includegraphics[width=\linewidth]{figures/centroid_inset10833.png}
%    \caption{A zoom-in of the line centroid positions of the  10830 triplet feature relative to the planet rest frame.}
%    \label{fig:HeliumZoom}
%\end{figure}

\begin{figure}
    \centering
    \subfloat{\includegraphics[width=5cm]{figures/centroid_overview10833.png} }
    \hskip-3em
    \subfloat{\includegraphics[width=4cm]{figures/centroid_inset10833.png}}
    \caption{Line centroid positions of the  10830 triplet.  \emph{left}: The overview panel shows a slight blueshift relative to the stellar restframe, and a weak excess blueshift trend after planet egress. \emph{right:} The detailed zoom-in of the in-transit phase shows a redshift relative to the planet restframe at ingress and a blueshift relative to the planet restframe near egress.  The line-of-sight velocity distribution of 2-3 \AA means that the gas distribution exhibits both advancing and receding lobes at all phases other than post-egress.}
    \label{fig:example}
\end{figure}
